Local Normalisation using the Empirical Null for Inspection of Additive Manufacturing using X-Rays

### 2019-04-09 reports/paper1/paper.tex
Revision

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed GLM \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.

It was assumed that the grey values were Normal, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Their estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ also respectively. Define the null hypotheses to be
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
which are tested against
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large}.

To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{parzen1962on, friedman2001elements}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of pixels in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  } \ .
\end{equation}
All the normalised test statistics were converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
\end{equation}
and was used in the \cite{benjamini1995controlling} (BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.

@@

Line filtering was done from left to right. At the start on the far left, an initial value of the median of all the pixels in the kernel was used. For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as a initial point. This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.

@@

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example. in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects. The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.

@@

The contamination is a nuisance because the test statistics have larger variance and larger values at the two corners. This cause an inflation in false positives which leads to incorrect inference.

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulate example, it is about $r>54$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

Preserving FDR is important because it keeps the FDR consistent before and after filtering. For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%. It appeared a large kernel radius helped preserve FDR control after filtering in these examples.

>>>>

The variance model, $\widehat{\variance}\left[\text{scan}_{x,y}\right]$ has a linear relationship between the variance and the grey value \citep{yang2010noise}. The fitting of the model was done using the held out replicated x-ray images of the 3D printed sample. These replicated x-ray images were manually segmented. This provided variance-mean data, where each pixel is a data point, and was used to fit the variance model. The model used was a gamma distributed generalised linear model \citep{nelder1972generalized, mccullagh1984generalized} with an identity link. The variance was predicted using the grey value in the \texttt{aRTist} simulation as the predictor variable when working out the test statistics.

It was assumed that the grey values were Normal, therefore the test statistics should be approximately Normal as well. Let the test statistic of the pixel at position $(x,y)$ be
\begin{equation}
Z_{x,y}\sim\normal(\mu_{x,y},\widehat{\sigma}_{0,x,y}^2)
\end{equation}
for $x=1,2,\cdots,W$ and $y=1,2,\cdots,H$. $\mu_{0,x,y}$ and $\sigma_{0,x,y}$ are the null mean and null standard deviation at position $(x,y)$ respectively. Their estimates are $\widehat{\mu}_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ also respectively. Define the null hypotheses to be
\begin{equation}
  H_{0,x,y}:\mu_{x,y}=\widehat{\mu}_{0,x,y}
\end{equation}
which are tested against
\begin{equation}
  H_{1,x,y}:\mu_{x,y}\neq\widehat{\mu}_{0,x,y} \ .
\end{equation}
The empirical null filter aims to obtain the estimators $\widehat{\mu}
_{0,x,y}$ and $\widehat{\sigma}_{0,x,y}$ for all $x$ and $y$. This is based on the empirical null \citep{efron2004large} where hypothesis testing is done by comparing a test statistic with the empirical distribution of the majority of the test statistics rather than a specified null distribution.

To obtain the estimates, a circular kernel with radius $r$ was centred at $(x,y)$. All the pixels captured by the circular kernel and the region of interest (ROI) were pooled together to obtain a kernel density estimate \citep{parzen1962on, friedman2001elements}
\begin{equation}
\widehat{p}_{Z_{x,y}}(z) = 
\frac{1}{nh}
  \sum_{i,j\in K_{x,y}}\phi\left(
    \dfrac{z_{i,j}-z}{h}
  \right)
\end{equation}
where $K_{x,y} = \text{kernel centred at }(x,y) \cap \text{ROI}$, $n$ is the number of pixels captured by $K_{x,y}$, $\phi(z)$ is the probability density function of a standard Normal random variable and $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = (0.9n^{-1/5}\ + 0.16) \times \text{min}\left(s_{x,y},\text{IQR}_{x,y}/1.34\right)
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_{x,y}$ and $\text{IQR}_{x,y}$ are the sample standard deviation and sample interquartile range of the test statistics in $K_{x,y}$, similar to \cite{silverman1986density, sheather2004density}. The estimates were obtained by solving
\begin{equation}
\widehat\mu_{0,x,y} = \text{argmax} \widehat{p}_{Z_{x,y}}(z)
\end{equation}
using the Newton-Raphson method and
\begin{equation}
  \widehat{\sigma}_{0,x,y} = \left[
    \left.
      -\dfrac{\partial^2}{\partial z^2}\ln\widehat{p}_{Z_{x,y}}(z)
    \right|_{z=\widehat{\mu}_{0,x,y}}
  \right]^{-1/2}
\end{equation}
\citep{efron2004large}. The test statistics were normalised using
\begin{equation}
  T_{x,y} = 
  \dfrac{
    Z_{x,y}-\widehat{\mu}_{0,x,y}
  }
  {
    \widehat{\sigma}_{0,x,y}
  } \ .
\end{equation}
All the normalised test statistics were converted to $p$-values
\begin{equation}
  p_{x,y} = 2(1-\Phi(|t_{x,y}|))
\end{equation}
and was used in the \cite{benjamini1995controlling} (BH) procedure at the 5\% FDR level to classify pixels as positive or not for defects.

@@

Line filtering was done from left to right. At the start on the far left, an initial value of the median of all the test statistics in the kernel was used. For the following pixel to the right, the empirical null mean of the neighbouring left pixel was used as the initial point. This was chosen as it was assumed the empirical null mean would vary slowly and smoothly spatially.

@@

Contamination is the result of a linear transform of the test statistics $Z_{x,y}$. For example in this experiment, the image was multiplied by 2 and a gradient was added to it. Suppose the image does contain defects, then an example of a resulting distribution is
\begin{align}
  Z_{x,y}|H_{0,x,y}&\sim\normal(\mu_{0,x,y},2^2)
  \\
  Z_{x,y}|H_{1,x,y}&\sim\normal(2\mu_1+\mu_{0,x,y},2^2)
\end{align}
where $\mu_{0,x,y}=0.01(x-x_0)+0.01(y-y_0)$ and $(x_0,y_0)$ is the centre of the image. This was used in this experiment to simulate a contaminated image with defects. The contaminated square defected image is shown in Figure \ref{fig:inference_defectSquare2Example}.

@@

The contamination is a nuisance because the test statistics will have larger variance and larger values at the two corners. This will cause an inflation in false positives which will lead to incorrect inference.

Literature, such as \cite{efron2004large} and \cite{schwartzman2008empirical}, suggest that, as a rule of thumb, the proportion of non-null statistics should not be larger than $0.1$ to satisfy some assumptions made for the empirical null. In this simulated example, it is about $r>54$. A kernel too small would treat the defects as null, making them difficult to detect.

@@

Keeping the FDR consistent before and after filtering is desirable so that the FDR is kept controlled at a specified level after filtering. For large enough kernel radius, the FDR was controlled at around, perhaps a bit below, 5\%. It appeared a large kernel radius helped preserve FDR control after filtering in these examples.
